{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-02 Paper/main.tex
Rendering

	 This setup is opposing to the often used penalized functional regression as described by \citep{Goldsmith_2011} in which an explicit smoothness constraint $\lambda$ is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high. This would avoid the heavy computing of validating the best value for $K$ which we will conduct in the simulation. To provide intuition in this approach, let 
	 \begin{equation}
	 	PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} (Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt)^2 + \lambda * \int (D^m\beta(t))^2 dt
	 \end{equation}
	 denote the penalized residual sum of squares as notated by \cite{ramsay_functional_2005} for the derivative of order $m$. A typical choice is the second derivative as highly variable functions are expected to yield large second derivatives and therefore a larger penalty. The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be archived by different criteria as shown in \cite{ThomasLee_2003}

>>>>

	 This setup is opposing to the often used penalized functional regression as described by \cite{Goldsmith_2011} in which an explicit smoothness constraint $\lambda$ is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high. This would avoid the heavy computing of validating the best value for $K$ which we will conduct in the simulation. To provide intuition in this approach, let 
	 \begin{equation}
	 	PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} (Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt)^2 + \lambda * \int (D^m\beta(t))^2 dt
	 \end{equation}
	 denote the penalized residual sum of squares as notated by \cite{ramsay_functional_2005} for the derivative of order $m$. A typical choice is the second derivative as highly variable functions are expected to yield large second derivatives and therefore a larger penalty. The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be archived by different criteria as shown in \cite{ThomasLee_2003}
